\documentclass{beamer}
\usepackage[utf8]{inputenc}

\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}


\title[LING 120]{LING 120: Language and Computers}
\subtitle{Semester: FALL 2017}

\date{21 Aug 2017}

\institute{Iowa State University, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

\begin{frame}
\frametitle{Class outline}
\begin{itemize}
\item Introductions %15min
\item Course objectives %5min
\item Course logistics %5min
\item Syllabus, Assignments and Deadlines. %5min
\item Course policies %5min
\item Canvas %5min
\item Pre-course questionnaire %10min
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
\Large Introductions
\end{center}
\end{frame}

\begin{frame}
\frametitle{About me}
\begin{enumerate}
\item In ISU as Asst. Professor since January 2016.
\item Prior to that, PhD student in Computational linguistics, in Germany.
\item Other education: Masters in Computer Science and Engineering, Bachelors in Electronics and Communication Engineering.
\item Other details: 3 years as a software developer in India.
\item Other courses I teach: Intro to Python, NLP, Data Science courses; Statistical NLP; Technical Communication
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{About you?}
\begin{enumerate}
\item Name
\item Discipline and Year
\item What is your idea about this course? 
\end{enumerate}
\end{frame}

%few slides on background

\begin{frame}
\frametitle{}
\begin{center}
\Large What is this course about?
\end{center}
\end{frame}

\begin{frame}
\frametitle{Some questions to think about }
\begin{itemize}
\item How is language different from - say numbers or images or music - for a computer?
\item What does a computer see where we see a coherent piece of writing that means something?
\item What does it see when you listen to a recorded speech on a given topic?
\item What is the intuition behind all those language processing software we see and use in daily life? (e.g., spell-grammar check, machine translation, Siri kind of tools etc)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Course Objectives}
\begin{itemize}
\item Give an overview of various real-world challenges and applications that involve computers working with human language
\item Discuss how language technology works by focusing on a few applications
\item Give enough conceptual background to understand language technology and processing.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
Course Logistics
\end{center}
\end{frame}

\begin{frame}
\frametitle{Time and location}
\begin{itemize}
\item Course meets on:
\begin{itemize}\itemsep1ex
\item Monday, Fridays: 2:10-3 PM, E Hall 0111
\item Wednesday: 2:10-3pm, Ross 137
\end{itemize}
\item Office Hours:  
\begin{itemize}\itemsep1ex
\item Monday, Wednesday: 1-2 PM, Ross 331 (My office room).
\end{itemize}
(Please send an email if you want to meet)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Text Book}
You are recommended to have a copy of the following book: 
\begin{enumerate} 
\item Language and Computers, by Dickinson, Brew and Meurers. 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Course Format}
\begin{itemize}
\item Credits: 3
\item Course website: on Canvas (new for me too!).
\item Format: weekly meetings
 \begin{itemize}
  \item presentations and discussions
  \item pre-assigned readings for the week
  \item in-class writing exercises
 \end{itemize}
 \item grading
  \begin{itemize}
 \item weekly graded assignments
\item Mid-term (group) and Final exam (individual)
\end{itemize}
 \end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
Syllabus, Deadlines etc 
\end{center}
\end{frame}

\begin{frame}
\frametitle{Syllabus - Topics}
\framesubtitle{Details on Canvas}
\begin{enumerate}
\item Introduction
\item Encoding human language on computers (topic for Assignment 1)
\item Writers aids on computers (topic for Assignment 2)
\item Intelligent Tutoring Systems
\item Search and Information Retrieval (topics for Assignment 3)
\item Natural Language Processing - an overview of challenges, and applications (topic for Assignment 4)
\item Text Classification (topic for Assignment 5)
\item Interactive Dialogue Systems
\item Automatic Speech Recognition (topics for Assignment 6)
\item Machine Translation 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Scheduling}
\framesubtitle{Details on Canvas}
\begin{itemize} 
\item For class by class schedules - check Canvas. 
\item Important deadlines:
(note: all deadlines end at 11:59 pm on that day, and are typically on Saturdays for assignments and Wednesdays for other exams)
\begin{enumerate}
\item Assignment 1: 8 September 2017
\item Assignment 2: 23 September 2017
\item Assignment 3: 7 October 2017
\item Mid-term: 11th October 2017 (midterms presentations on Monday and Wednesday that week)
\item Assignment 4: 21st October 2017
\item Assignment 5: 4th November 2017
\item Assignment 6: 18th November 2017
\item Final exam: 13th December 2017
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
\Large Course Policies
\end{center}
\end{frame}

\begin{frame}
\frametitle{Grading Policy}
\begin{itemize}
\item Nature of work: 6 assignments (10*6 = 60\%), mid-term (20\%) and final exam (20\%).
\item Mid-term is a group oral presentation in the class.
\item Final exam is a take home exam which involves either a report or small coding project if you have a programming background and want to make use of it.
\item Topics for mid-terms and final exam will be announced later.
\item All assignments are already uploaded on Canvas.
\item Plus/minus grading will be used
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Attendance Policy}
\begin{itemize}
\item You require a minimum of 80\% attendance to pass the course with full credits.
\item If you drop below that, your grade will reduce by one grade point for each 5\% reduction 
\\ (i.e., If you got A before taking attendance into account, 75-80\% attendance will give you a A-, 70-75\% attendance will give you a B+, and so on)
\item I don't take attendance by roll-call, but will give an exercise in the class for each class day (can be submitted online). Your completion of these counts as attendance for that day.
\item Absentees can browse the course slides, finish the exercise, and still get attendance if they worry about losing the grade because of too many missing classes.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{General behavior}
\begin{itemize}
\item Come to class on time.
\item Avoid doing other course work in this class.
\item Avoid unnecessary browsing in the class.
\item Emails: Please write professionally. Address me by name. Not "Hello" but "Hello Sowmya" or "Hello Dr Vajjala" or "Hello Professor" or whatever.  I promise to address properly as well. 
\item Don't keep talking loudly between yourselves in the class.
\item Let us respect each other and behave professionally.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Feedback to me}
\begin{itemize}
\item This is a diverse group. I may appear to ignore one group or the other sometimes. If it happens once, forgive and forget. If it persists, please talk to me directly, or leave anonymous feedback at: \url{http://goo.gl/AsF6cX} or leave a paper feedback in my mailbox at Ross 206.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Other Issues}
\begin{itemize}
\item Disability accommodation: Please speak to Disability Resources Office (DRO) to officially request an accommodation. Send me a copy of the accommodation letter, if you already have one.
\item Course policies on other issues: refer to Course Policies document on Canvas
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
\Large Canvas tour and syllabus document overview
\end{center}
\end{frame}

\begin{frame}
\frametitle{}
\begin{center}
\Large Please complete the pre-course questionnaire \\ \small (your attendance for today)
\end{center}
\end{frame}

\begin{frame}
\frametitle{Next Class ..} 
\begin{itemize}
\item Topic: Encoding text on computers- an overview
\item Readings: Read up to Section 1.3 in Chapter 1 in the textbook.
\item To Do: Browse the canvas course website and get back if you have questions
\item To Do: Have a look at the syllabus document.
\item If you have never heard of binary numbers, watch these videos (atleast the "conversion from decimal to binary" 4 min video) from Khan Academy (\url{https://goo.gl/o2dgdd}) before wednesday to understand the class fully.
\end{itemize}
\end{frame}

\end{document}

