\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subfig}
\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}


\title[LING 120]{LING 120, Fall 2017 \\ Language and Computers}

\date{27 September 2017}

\institute{Iowa State University, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

\begin{frame}
\frametitle{Class outline}%5minutes
\begin{enumerate}
\item Regular Expressions: brief tutorial
\item Group exercise
\end{enumerate}
\end{frame} %\item Assignment 3 Description - do this on Monday

\begin{frame}
\frametitle{Last class' Exercise}
\begin{itemize}
\item Consider this passage: \\ \small 
\textit{This assignment consists of two questions and carries a to-
tal of 10 marks. Submit your assignment as a *PDF* file and name it as:
your first name–your last name.pdf Late submissions are allowed, but will
not be awarded full credit.} \normalsize
\item I want to identify the number of times \textbf{s} appeared at the beginning of the word in this. I use the regular expression: \textbackslash Ws
\item What is the precision and what is the recall for this regular expression in terms of achieving its goal? \pause
\item What will the expression capture? \pause (s in submissions).
\item Ideally, it should capture Submit as well (although my question was ambiguous).
\item Now, what is Precision and Recall for both cases?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions: Recap from Monday}
\begin{itemize}
\item Regular expressions are a kind of language to describe patterns that follow a structure in text data
\item E.g., words that start with a letter, a particular pattern of spelling (e.g., ss appearing 2 times in a word), a pattern of words (e.g., not only ... ... but also), phone numbers, all urls in a wikipedia page etc.
\item Some basics we saw on Monday: usage of +, *, ., $|$, $[:alpha:], [:digit:], [:punct:]$ 
\item All programming languages, and lot of software such as MS Word support regular expression based search in documents.
\end{itemize}
See also: \url{http://www.petefreitag.com/cheatsheets/regex/}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions in real life}
\begin{itemize}
\item Manning's video: \url{https://www.youtube.com/watch?v=RGLldper5II}
\item \url{https://www.linkedin.com/pulse/regular-expressions-real-life-lyle-wincentsen/}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Grep and Egrep - tools to search large files/folders using regular expressions}
\begin{itemize}
\item Available by default on Unix based operating systems (Mac, Ubuntu etc)
\item Windows 10 perhaps supports it (I don't know - you should tell me!) \pause
\item Brief demo of using egrep:
\begin{verbatim}
egrep 'Stockmann' pg2446.txt
egrep '[[:digit:]]' pg2446.txt
egrep 'Petra|Horster' pg2446.txt
egrep 'Petra|Horster' pg2446.txt | wc
egrep 'th(e|i)s' pg2446.txt
egrep 'th(e|i)s*' pg2446.txt
\end{verbatim}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions: Practice}
\framesubtitle{Attendance exercise -answer on Canvas}
Work in groups of 3 people, download pg2446.txt from \url{https://goo.gl/gSnhGD}, and answer the following questions using regular expressions.
\begin{itemize}
\item Whose name occurs more at the beginning of a line - Dr Stockmann or Mrs Stockmann? How many times?
\item What is the difference between \textit{egrep 't.s' pg2446.txt} and \textit{egrep 't.*s' pg2446.txt}?
\item In general, what will the pattern \textit{joh?n} identify? How will you verify?
\item What will \textit{egrep -o 'Stockmann' pg2446.txt} do? Why? What happens if you remove the -o?
\item How many times do Stockmann and Petra appear in the same line in this file?
\end{itemize}
Note: Regular expressions cheatsheets, egrep help can be found by searching online. 
\end{frame}

\begin{frame}
\frametitle{Next Class}
\begin{itemize}
\item Conclusion of Topic 4
\item Time to decide on your Midterm topics
\item To do: Know your mid-term team members. Start thinking about a topic.
\end{itemize}
\end{frame}

\end{document}
