\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}

\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}


\title[LING 120]{LING 120: \\ Language and Computers}
\subtitle{Semester: Fall '17}

\date{15 November 2017}

\institute{Iowa State University, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
\item quick recap and Discussion about yesterday's exercise
\item Group exercise + presentation on machine translation
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Challenges for Machine Translation: Recap}
\begin{itemize}
\item Each word can have multiple meanings, so mapping words one-one between languages is not possible.
\item How words are formed between languages
\item What is the order of words
\item Words that don't seem to translate
\item Words that seem to come up in translation that do not exist in original
\item Issues such as: articles don't exist in Telugu, but they do in English. Kinship words are more fine grained in Telugu than English etc.
\item Stylistic and cultural differences - which can make even manual translation difficult
\item Metaphor is even difficult - same metaphors need not exist in both languages
\item Poetry with rhyme - what if those words don't rhyme in Target language?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{yesterday's exercise}
In this course so far, where is the idea of n-grams useful among the topics we discussed? Do you think they are useful in Machine Translation too? 
\end{frame}

\begin{frame}
\frametitle{Discussion about yesterday's exercise}
\begin{itemize}
\item n-grams are useful for two aspects of machine translation
\begin{itemize}
\item Map phrases in one language to another
\item Decide what is the most appropriate ordering of words in the translated output, what is grammatical, what is more natural for that language etc. 
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Rest of the class today}
\begin{itemize}
\item A group exercise: Form into groups of 3 people (such that at least one person knows one non-English language)
\item Two questions:
\begin{itemize}
\item What other translation software exist apart from google translate?
\item Take a language pair (e.g., English-German, English-Chinese etc). Use google translate and try translating a few sentences. Do also the reverse translation. (Chinese-English, German-English etc.).
\item Try to understand how it works (e.g., where it works, where it fails, if I take an English sentence and translate to Chinese, and translate that Chinese one back to English, are they same? etc) 
\item After 20 minutes, each team should summarize their observations - you can use 2--3 slides if you want (share the slides on Canvas forum for today and present to the class).
\end{itemize}
\item This is your attendance. 
\end{itemize}
\end{frame}

\end{document}
