\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}

\author[Sowmya Vajjala]{Instructor: Sowmya Vajjala}

\title[LING 120]{LING 120: \\ Language and Computers}
\subtitle{Semester: Fall '17}

\date{8 December 2017}

\institute{Iowa State University, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}\titlepage
\end{frame}

%Dialog systems, machine translation, others - impact on society questions
%Exercise: Spelling suggestions NACLO exercise and Discussion
%Future reference - coruses, books etc.
%Reminder about finals.
%Wish them good luck!

\begin{frame}
\frametitle{Today's class}
\begin{itemize}
\item Reminder about Final submission date
\item Continuation of the discussion on language technologies and impact on society
\item Group exercise on Spelling suggestions (20-25 min)
\item Pointers for further study
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Final Submission}
\begin{itemize}
\item Date: 13th December (Read instructions carefully before submitting)
\item Grades: You can see them after the official exams week
\item Course Evaluations: Do it if you did not do on Wednesday. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{In the coming few slides: }
\begin{itemize}
\item I will do a quick 1-2 sentence summary of a topic, and ask questions about the impact of that topic on our society.
\item Impact can be in terms of new gadgets in our hands, new jobs, new ways to learn, making life comfortable/better - anything.
\item I will ask one person per topic - others can also join and contribute answers.
\item Note: Make notes. It will be a useful exercise to submit your final exam writeup.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Topic 6: Dialog Systems}
\begin{itemize}
\item What did we discuss: different types of dialog systems, how to evaluate them, what is the state of the art? 
\item Questions:
\begin{enumerate}
\item How are these relevant in the current day society?
\item What kind of applications came up because of these technologies, which could not have happened before?
\item How do these applications impact our society? 
\end{enumerate} 

\pause \item Among all these topics, this is the single topic which saw big developments in the past 5 years, and will continue. So, if you ask me - this is the most suitable area to enter now and still make a mark. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Topic 7: Speech Recognition, Speech Synthesis}
\begin{itemize}
\item What did we discuss:  How do they work, What do we need to develop such systems, how do we evaluate?
\item Questions:
\begin{enumerate}
\item How are these relevant in the current day society?
\item What kind of applications came up because of these technologies, which could not have happened before?
\item How do these applications impact our society? 
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Topic 8: Machine Translation}
\begin{itemize}
\item What did we discuss:  Challenges in developing MT systems, General ideas behind current approaches, evaluation
\item Questions:
\begin{enumerate}
\item How are these relevant in the current day society?
\item What kind of applications came up because of these technologies, which could not have happened before?
\item How do these applications impact our society? 
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Other Smaller Topics}
\begin{itemize}
\item What did we discuss:  General tasks in NLP (POS tagging, parsing, word sense disambiguation etc.), Cryptography and Language
\item Questions:
\begin{enumerate}
\item How are these related to other topics in this class?
\item What (in your view) is the kind of background needed to work in the intersection of language processing and computer science and build the applications we discussed in this class?
\end{enumerate}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\centering
Work in groups and solve this small puzzle in 10-15 minutes. Whoever finishes first should explain their method as well. \bigskip
\footnotesize 
\pause \\ problem: \url{http://nacloweb.org/resources/problems/2009/N2009-B.pdf}
\\ solution: \url{http://nacloweb.org/resources/problems/2009/N2009-BS.pdf}
\end{frame}

%Courses, Books etc.
\begin{frame}
\frametitle{Pointers for Further Study}
\begin{itemize}
\item Courses: Look for course descriptions about Natural Language Processing, Computational Linguistics etc. Most universities have courses on these topics. 
\item Books: Speech and Language Processing, by Jurafsky and Martin (draft chapters are online for free)
\item Websites: nacloweb.org- for challenges, aclweb.org for research articles, all those different links I gave you during the class.
\item in ISU, there are a couple of courses in Linguistics and CS departments that are relevant. 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{}
\centering
Good luck for your future! Really enjoyed teaching this class!
\end{frame}



\end{document}
