\documentclass[11pt,a4paper]{article}
\usepackage[greek,english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{url}

\begin{document}
\begin{center}
  Fall Semester 2017 \\ Iowa State University\\[3ex]
  {\large LING 120 - Language and Computers}\\[3ex]
  \textbf{Assignment 1} \\ \textbf{Submission Deadline: 8 SEP 2017, end of the day}
\end{center}


\paragraph{Instructions:} This assignment consists of two questions and carries a total of 10 marks. Submit your assignment as a *PDF* file and name it as: your\_first\_name--your\_last\_name.pdf Late submissions are allowed, but will not be awarded full credit.

\section*{Question 1 - 4 marks} 
Your first question has three parts, and is on encoding text on a computer.
\begin{enumerate}
\item Write "America" in ASCII, with both decimal number and binary representation.
\item What are the Unicode character ranges for Telugu, Japanese, Russian?
\item Get the Greek translation for the word "Computer" from Google translate. Now, use this website: \url{http://r12a.github.io/apps/conversion/}
and get the ASCII, UTF-8 and UTF-16 representations of this Greek word. Do they all look the same, or different? Why?
\end{enumerate}

\section*{Question 2 - 6 marks}
Your second question is something similar to Question 5 in Chapter 1. Install Praat or any other speech analysis software kit on your computer. 3 speech samples (from: \url{http://codewelt.com/proj/speak}) are attached with this assignment description. Compare and contrast the spectrograms of these 3 samples by describing how what was said in the samples correspond to the spectrogram, and what kind of differences exist between the spectrograms.

\end{document}

%Have a discussion on this assignment once the grades are uploaded. 