\documentclass[11pt,a4paper]{article}
\usepackage{url}

\begin{document}
\begin{center}
  Fall Semester 2017 \\ Iowa State University\\[3ex]
  {\large ENGL 120 - Language and Computers}\\[3ex]
  \textbf{Assignment 6} \\ \textbf{Submission Deadline: 18 NOV 2017, end of the day}
\end{center}

\paragraph{Instructions:} This assignment consists of two questions and carries a total of 10 marks. Submit your assignment as a *PDF* file and name it as: your\_first\_name--your\_last\_name.pdf Late submissions are allowed, but will not be awarded full credit. 

\section*{Question 1} 
On your computer or on your mobile phone, there will be a software that can conduct a conversation with you (Siri, Google Assistant, Cortana, Alexa etc). Choose any one system, interact with it briefly and write an analysis addressing issues such as what they do well, where they fail, how they work with accents, do they catch impoliteness? Are they polite or impolite with you? etc.

\section*{Question 2}
%How do you evaluate a dialogue system?
Let us say there are four applications:
\begin{itemize} 
\item a system that generates weather reports automatically from tables of data indicating temparature, humidity etc.
\item a system that looks at a news article and creates a one paragraph summary by itself?
\item a chat bot that trouble shoots laptop servicing problems
\item ELIZA like bot that holds conversations with you.
\end{itemize}
- Which among these four is relatively easy to make? Why? How would you evaluate all these systems? What part of evaluation is common for all systems, and what part is specific for each system?
\end{document}
